Paper Figures and Text

### 2022-11-21 Fish Data Analysis/Paper_Figures.qmd
Adding Velocity Dot Product

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
```

@@

```{r}
raw_comp_data <- read.csv("Data/Fish_Raw_Comp_Values.csv")
raw_comp_data <- na.omit(raw_comp_data)

@@

velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10)
```

@@

ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff)))+
  #geom_point(alpha = 0.01)+
  geom_violin() +
  theme_classic()

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
```

@@

```{r}
raw_comp_data <- read.csv("Data/Fish_Comp_Values.csv")
raw_comp_data <- na.omit(raw_comp_data)

@@

velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10) %>% filter(Fish1_Speed < 5) %>% filter(Fish2_Speed < 5)  %>% filter(Flow == "Still Water")

velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>% filter(round_Distance != 8)

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff))) %>%
                                               ungroup()
```

```{r}
ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none") +
  ylab("Correlation Strength")+
  xlab("Distance (BL)")
```

@@

ggplot(velocity_cor_data, aes(x = Fish1_Speed, y = Fish2_Speed))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = "lm")+
  theme_classic()+ 
  theme(legend.position = "none")

ggplot(velocity_cor_data, aes(x = Distance, y = Fish1_Speed*Fish2_Speed))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none")

cor.test(velocity_cor_data$Fish1_Speed,velocity_cor_data$Fish2_Speed)

ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff), 
                                                                color = Flow_Ablation_Darkness))+
  geom_violin()+
  theme_classic()

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Speed_Diff, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_errorbar(aes(ymin = mean_Speed_Diff-sd_Speed_Diff, ymax = mean_Speed_Diff+sd_Speed_Diff),
                position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_classic()

speed_diff_glm <- glm(Speed_Diff ~ round_Distance * Flow_Ablation_Darkness, data = velocity_cor_data)
Anova(speed_diff_glm)

#emmeans(speed_diff_glm, specs = pairwise ~ Flow_Ablation_Darkness)
#emmeans(speed_diff_glm, specs = pairwise ~ round_Distance)
